# lockr <a href = "https://danielvartan.github.io/lockr/"><img src = "man/figures/logo.svg" align="right" width="120" /></a>

<!-- quarto render -->

<!-- Install the package before rendering this file: `devtools::install()` -->

```{r}
#| label: setup
#| include: false

library(lockr)

library(badger)
library(here)

badge_codecov() |> invisible() # To avoid unnecessary messages.

source(here("R", ".setup.R"))
```

<!-- badges: start -->
```{r}
#| echo: false
#| output: asis
#| message: false
#| warning: false

cat(
  badge_repostatus("active"),
  badge_github_actions(action = "R-CMD-check.yaml"),
  badge_codecov(),
  badge_license(
    license = "GPLv3",
    color = "bd0000",
    url = "https://www.gnu.org/licenses/gpl-3.0",
    alt = "GNU GPLv3 License"
  ),
  badge_custom(
    x = "Contributor%20Covenant",
    y = "3.0",
    color = "4baaaa",
    url = "https://www.contributor-covenant.org/version/3/0/code_of_conduct/",
    alt = "Contributor Covenant 3.0 Code of Conduct"
  )
)
```
<!-- badges: end -->

## Overview

`lockr` is a simple and user-friendly R package designed for encrypting and decrypting files.

## Installation

You can install `lockr` using the [`remotes`](https://github.com/r-lib/remotes) package:

``` r
# install.packages("remotes")
remotes::install_github("danielvartan/lockr")
```

## Usage

`lockr` usage is very straightforward. The main functions are:

- [`lock_file`](https://danielvartan.github.io/lockr/reference/lock_file.html): Encrypt a file.
- [`unlock_file`](https://danielvartan.github.io/lockr/reference/unlock_file.html): Decrypt a locked file.

Along with these, there are helper functions to facilitate key management and other tasks. Click [here](https://danielvartan.github.io/lockr/reference/) to see the full list of `lockr` functions.

## License

```{r}
#| echo: false
#| output: asis

cat(
  badge_license(
    license = "GPLv3",
    color = "bd0000",
    url = "https://www.gnu.org/licenses/gpl-3.0",
    alt = "GNU GPLv3 License"
  )
)
```

```text
Copyright (C) 2025 Daniel Vartanian

lockr is free software: you can redistribute it and/or modify it under the
terms of the GNU General Public License as published by the Free Software
Foundation, either version 3 of the License, or (at your option) any later
version.

This program is distributed in the hope that it will be useful, but WITHOUT ANY
WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A
PARTICULAR PURPOSE. See the GNU General Public License for more details.

You should have received a copy of the GNU General Public License along with
this program. If not, see <https://www.gnu.org/licenses/>.
```

## Contributing

```{r}
#| echo: false
#| output: asis

cat(
  badge_custom(
    x = "Contributor%20Covenant",
    y = "3.0",
    color = "4baaaa",
    url = "https://www.contributor-covenant.org/version/3/0/code_of_conduct/",
    alt = "Contributor Covenant 3.0 Code of Conduct"
  )
)
```

Contributions are always welcome! Whether you want to report bugs, suggest new features, or help improve the code or documentation, your input makes a difference.

Before opening a new issue, please check the [issues tab](https://github.com/danielvartan/lockr/issues) to see if your topic has already been reported.
